HyperLogLog: Exponentially Bad in Adversarial Settings

### 2021-12-17 docs/HLL_exp_bad/main.tex
fix appendix sections

\section{Further analysis of Flexswitches}\label{sec:flexswitch}

@@

\section{Proof of Theorem 8.1}\label{sec:proof} %ridiculous, but had to hard-code this reference

@@

\section{Breaking HLL-UHF}\label{sec:UHF}

>>>>

\subsection{Further analysis of Flexswitches}\label{sec:flexswitch}

@@

\subsection{Proof of Theorem 8.1}\label{sec:proof} %ridiculous, but had to hard-code this reference

@@

\subsection{Breaking HLL-UHF}\label{sec:UHF}
